---
title: "Brownlows Bets"
author: "iboni archie"
date: "summer 2021"
output: 
  html_document:
    number_sections: true
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
require(knitr)
source(file="BrLw.R")
```


<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->

# Introduction

## 1.1 Our strategy is to build a Function

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

 At the first day of class there are 35 students in Math Statistics class and professor Brownlow always proposes this bet to his students "I will wager $2 to your bet of $1 that at least two people in today's class have  the same birthday.  He tells me he has made that bet 637 times so far. Where do you think his profits are? Discuss this in a markdown document
 
Report git commit structure:
There are 3 questions and there should be at least 3 separate commits, at least one dealing with each of the 3 questions.
1. What are the fair odds for a bet on matching birthdays in a 35 person class.
2. For what size class is a 2:1 odds bet fair.
3. How much money would Brownlow be expected to end up with if the bets went as described.

# What are the fair odds  


<!--Decide on your methods:  In this section explain the approach you will take to attack the issue --- how will you decide on a likely estimate of professor Brownlow's earnings or losses after 637 bets. Also explain how you construct a 95% confidence interval about your estimate of his winnings !-->


##2.0.1
##start with 2.0

```{r}
BrLw(numClass = 35,odds=2.0,countoDo = 637)

```

If The professor used the odds 2/1 he would have about 220 to 240 bucks.  


```{r}
BrLw(numClass = 35,odds=3.0,countoDo = 637)

```

If the professor used the odds 3/1 he would have about 200 hundred dollars a slightly less than the 2/1 bet he would loose money in this bet than he would earn in the previous bet.    

```{r}
BrLw(numClass = 35,odds=4.0,countoDo = 637)

```
  
With an odd of 4/1 he is not making much money as he is lossing.    
  
```{r}
BrLw(numClass = 35,odds=5.0,countoDo = 637)

```
With a 5/1 odd he is losing money no profit. The best odd is a 2/1 odd he makes the most money there.  

# What size of class makes the 2:1 bet fair?    
<!--Explain and display the results of your method of coming up with the estimate of professor Brownlows betting profits!-->

## 3.1 try 34  

```{r} 
BrLw(numClass = 34,odds=2.0,countoDo = 637)

```
### 3.1.1 ok try 31  


```{r}
BrLw(numClass = 31,odds=3.0,countoDo = 637)

```

### 3.1.2 ok try 29



```{r}
BrLw(numClass = 29,odds=3.0,countoDo = 637)

```

### 3.1.3 ok try 28


```{r}
BrLw(numClass = 28,odds=2.0,countoDo = 637)

```


# In the class and payoff as described what is a 95% confidence interval for Brownlow's earnings?


```{r}
fbank=numeric()
for(j in 1:1000){
  
fbank[j] = BrLw(numClass = 35,odds=2.0,countoDo = 637)}
```

```{r}
hist(fbank)
t.test(fbank)
favstats(fbank)
```
## 4.1 we will run at the given conditions 100 and get a 95% confidence interval  



## 4.2 There are a 1000 numbers in the bank-we sort them and take the middle 95%

### 4.2 1 The interval is  





### confidenceinterval `r fbank[25]` to  `r fbank[975]`


```{r}
sortedBank <- sort(fbank)
low=sortedBank[25]
high=sortedBank[975]
                
```






















  
<!--Explain and display your method of coming up with a 95% confidence interval of  professor Brownlows winnings (or losings)-->


# Discussion and Conclusion

<!--Discussion and conclusion here.  If professor Brownlow is consistantly making or losing money how could he change his payout so that his profits center on zero?  Also discuss what size his class should be in order to have his current scheme balance at zero profit.!-->

